\documentclass[11pt]{article}

%A Few Useful Packages
\usepackage{marvosym}
%\usepackage{fontspec} 					%for loading fonts
%\usepackage{xunicode}
%\usepackage{xltxtra}
\usepackage{url}
\usepackage{parskip} 	
\usepackage{enumitem}

%other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
%\usepackage[big]{layaureo} 				%better formatting of the A4 page
% an alternative to Layaureo can be ** \usepackage{fullpage} **
\usepackage{supertabular} 				%for Grades
\usepackage{titlesec}					%custom \section
\usepackage{hyperref}

%Setup hyperref package, and colours for links

\usepackage[text={6in,9in},centering]{geometry}


%FONTS
%\defaultfontfeatures{Mapping=tex-text}
%%\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin}
%%%% modified for Karol Kozioł for ShareLaTeX use
%\setmainfont[
%SmallCapsFont = Fontin-SmallCaps.otf,
%BoldFont = Fontin-Bold.otf,
%ItalicFont = Fontin-Italic.otf
%]
%{Fontin.otf}
%%%

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}
%Tweak a bit the top margin
%\addtolength{\voffset}{-1.3cm}

%Italian hyphenation for the word: ''corporations''
\hyphenation{im-pre-se}

%-------------WATERMARK TEST [**not part of a CV**]---------------
\usepackage[absolute]{textpos}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

%WATERMARK TEST [**not part of a CV**]---------------
%\font\wm=''Baskerville:color=787878'' at 8pt
%\font\wmweb=''Baskerville:color=FF1493'' at 8pt
%{\wm 
%	\begin{textblock}{1}(0,0)
%		\rotatebox{-90}{\parbox{500mm}{
%			Typeset by Alessandro Plasmati with \XeTeX\  \today\ for 
%			{\wmweb \href{http://www.aleplasmati.comuv.com}{aleplasmati.comuv.com}}
%		}
%	}
%	\end{textblock}
%}

\pagestyle{empty} % non-numbered pages

%\font\fb=''[cmr10]'' %for use with \LaTeX command

%--------------------TITLE-------------
\par{\centering
		{\Huge \textsc{William Harrison}, Ph.D
	}\bigskip
%	\\
%	1238 Sunset Drive, Columbia, MO 65203
%	\\ 
%	\href{mailto:william.lawrence.harrison@gmail.com}{william.lawrence.harrison@gmail.com}
%	\\
%	\href{https://harrisonwl.github.io}{https://harrisonwl.github.io}
	\par}


\section{Contact}

\begin{tabular}{rl}
    \textsc{Address:}   & 3145 Fountain Park Blvd, Knoxville TN 37917 \\
    \textsc{Phone:}     & 573 268-7402\\
    \textsc{Email:}     & \href{mailto:william.lawrence.harrison@gmail.com}{william.lawrence.harrison@gmail.com}\\
    \textsc{Web:}       & \href{https://harrisonwl.github.io}{https://harrisonwl.github.io}
\end{tabular}

%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
\section{Education}

\begin{tabular}{rl}	
\textsc{May 2001} & 
Ph.D., Computer Science, \textbf{University of Illinois at Urbana-Champaign}.
\\
	&    Dissertation: ``Modular Compilers and Their Correctness Proofs.''
  \\
  & Committee Chairman:  Samuel Kamin

\\
\\
\textsc{June 1992}
    & M.S., Computer Science, \textbf{University of California, Davis}.
    \\ 
    & Thesis: ``Mechanizing the Axiomatic Semantics for a Programming 
    \\& \hspace{9ex} Language with Asynchronous Send and Receive in HOL.''
    \\
    & Thesis Advisor: Karl Levitt
%
\\
\\
%
\textsc{June 1986} &     B.A., Mathematics,   \textbf{University of California, Berkeley}.
\end{tabular}

%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
\section{Academic  \& Professional Appointments }

\begin{tabular}{r|p{11cm}}
 
\textsc{Aug 2019--Present} & {\bf Senior Cybersecurity Scientist}, Oak Ridge National Laboratory, Cyber \& Information Security Research Group (CISR)
\\
\multicolumn{2}{c}{}
\\[-1ex]

\textsc{Sep 2003--Jul 2019} & {\bf Associate Professor}, Department of Computer
Science,
University of Missouri at Columbia. Promotion and tenure 5/26/2009
\\
\multicolumn{2}{c}{}
\\[-1ex]


\textsc{Aug 2013--Jul 2014} & {\bf Visiting Scientist}, National Security Agency\\
\multicolumn{2}{c}{}
\\[-1ex]

\textsc{Apr 2011--present} & {\bf Director}, The Center for High Assurance Computing at the University of Missouri
\\
\multicolumn{2}{c}{}
\\[-1ex]


\textsc{Sep 2010--Aug 2013} & {\bf Research Consultant}, Pro-telligent, Inc. 
Arlington, VA
\\
\multicolumn{2}{c}{}
\\[-1ex]

\textsc{Jun 2000--Aug 2003} & {\bf Senior Research Associate \& Adjunct Professor}, Computer
Science Dept.,
Oregon Graduate Institute, Beaverton OR
\\
\multicolumn{2}{c}{}
\\[-1ex]

\textsc{Sep 2000--Dec 2000} & {\bf Senior Compiler Engineer (consultant)}, Reservoir
Laboratories, Portland, Oregon.
\\
\multicolumn{2}{c}{}
\\[-1ex]

\textsc{Aug 1999--May 2000} &
    {\bf Visiting Lecturer}, Department of Computer Science,
	Indiana University, Bloomington, IN 47401.
	\\
	\multicolumn{2}{c}{}
	\\[-1ex]
	
\textsc{Spring 1999} & 
	{\bf Visiting Lecturer}, Department of Computer Science,
	  University of Illinois at Urbana-Champaign, Urbana, IL.
\end{tabular}

%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
\section{Research Interests}

Reconfigurable computing and high-level synthesis; Hardware and Embedded system security;
Computer security and
language-based methods in security; Trustworthy computing; Formal methods (particularly with respect to
hardware/software codesign);  Programming language
design and implementation.

%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
\section{Personal Information}

\begin{itemize}[leftmargin=0mm]
\item[]  I am a US citizen.

%\item[]  I have a Top Secret/SCI security clearance.

\item[]  I am married to Amber Bradshaw, who is a ceramic artist.

\item[]  We have two children: Tegan and Caden (twins, 9 years old). 

\end{itemize}




%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
\section{Funding History}

\noindent{\bf Proposals Under Submission}

\begin{itemize}[leftmargin=0.0mm]
\item[]
{\bf Agency:} Office of Naval Research.
\\
{\bf Title:} High Assurance FPGA Design.
\\
{\bf Proposed Budget:} \$2,980,000.
\\
%{\bf Period:}   May 2016  --  August 2019.
%\\
{\bf Role:}    Collaborative research proposal with Dr. Gerard Allwein (US Naval Research Laboratory) and Professor Jason Bakos (University of South Carolina, Computer Science \& Engineering).

\end{itemize}


\noindent{\bf Active Grants and Contracts}

\begin{enumerate}[leftmargin=0.0mm]
\item
{\bf Agency:} US Naval Research Laboratory.
\\
{\bf Title:} Mechanizing the Metatheory of the ReWire Language with Applications.
\\
{\bf Amount:} \$720,000.
\\
{\bf Period:}   May 2016  --  August 2019.
\\
{\bf Role:}    Sole  Principal investigator.

\item
{\bf Agency:} US Naval Research Laboratory.
\\
{\bf Title:} Integrated Formal Methods for Secure FPGA Development.
\\
{\bf Amount:} \$300,000.
\\
{\bf Period:}   January 2019  --  December 2021.
\\
{\bf Role:}    Sole  Principal investigator.
\end{enumerate}


\noindent{\bf Completed Grants and Contracts}

\begin{enumerate}[leftmargin=0.0mm]
\item
{\bf Agency:} US Naval Research Laboratory.
\\
{\bf Title:} Type-Based Analysis of Security Flows in ReWire Circuit Specifications.
\\
{\bf Amount:} \$99,999.
\\
{\bf Period:}   October 2014  --  October 2015.
\\
{\bf Role:}     Sole Principal investigator.



\end{enumerate}

\newpage
%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
%\section{Funding History (cont'd)}

\begin{enumerate}[leftmargin=0.0mm,resume]
\item  {\bf Agency:} National Security Agency.\\
               {\bf Title:} Inter-agency Personnel Agreement.\\
               {\bf Amount:} \$144,190.00 \\
               {\bf Period:} August 2013 -- August 2014.

\item
{\bf Agency:} Department of Defense, Federal Voting Assistance Program (FVAP).
\\
{\bf Title:} Secure Ballot Delivery to UOCAVA Voters (Uniformed, Overseas, Citizens Absentee Voters). 
\\
{\bf Amount:} \$550,000.
\\
{\bf Period:} May 1, 2012 -- April 30, 2015.
\\
{\bf Role:} Collaborative research with Dr. Dale Musser of MU's Information Technology Program and Dr. Keith Politte of MU's Reynolds School of Journalism. 

\item
{\bf Agency:} Department of Education.
 ~\\
{\bf Title:} Graduate Assistance in Areas of National Need (GAANN) Fellowships.
\\
{\bf Amount:} \$240,000.
\\
{\bf Period:} September 1, 2011 -- May 15, 2015.
\\
{\bf Role:} Co-Investigator. Two of my Ph.D students (Adam Procter and Christopher Hathhorn) were GAANN fellows. 

\item
{\bf Agency:} National Science Foundation.
\\
{\bf Title:} CAREER: Automated Synthesis of High Assurance Security Kernels.
\\
{\bf Amount:} \$450,000.
\\
{\bf Period:}   June 1, 2008  --  May 31, 2013.
\\
{\bf Role:}      Sole Principal Investigator.

\item
{\bf Agency:} Office of the Asst. Secretary of Defense for Research and Development (ASD(R\&E)).
\\
{\bf Title:} Understanding Security Flows in the Many Core Era.
\\
{\bf Amount:} \$1,370,000.
\\
{\bf Period:}   January 2012  --  July 2015.
\\
{\bf Role:}      Principal Investigator. Collaborative Research with Dr. David Andrews (University of Arkansas) and Dr. Gerard Allwein (NRL).

\item
{\bf Agency:} US Naval Research Laboratory.
\\
{\bf Title:} MILS Hardware and Its Formal Methods-based Security.
\\
{\bf Amount:} \$810,000.
\\
{\bf Period:}   April 2008  --  April 2011.
\\
{\bf Role:}      Principal Investigator. Collaborative Research with Dr. David Andrews (University of Arkansas) and Dr. Gerard Allwein (NRL).


\item
{\bf Agency:} Department of Defense through OHSU/OGI.
\\
{\bf Title:} System Information Assurance II
\\
{\bf Amount:} \$31,703 
\\
{\bf Period:}   July 1, 2004  --  July 31, 2006
\\
{\bf Role:}      Principal Investigator

\item
{\bf Agency:} University of Missouri-Columbia Research Council.
\\
{\bf Title:} Big Twelve Faculty Fellowship
\\
{\bf Amount:} \$2,400
\\
{\bf Period:}   June 1, 2005  --  August 31, 2005 
\\
{\bf Role:}      Sole Principal Investigator
\end{enumerate}

\newpage
%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
\section{Peer-reviewed Publications}

%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
\noindent{\bf{Book Chapters}}

\begin{enumerate}[leftmargin=0.0mm]
\item
Gerard Allwein and William L. Harrison.
\newblock Distributed Modal Logic.
\newblock {\it J. Michael Dunn on Information Based Logics, Book Chapter, pages 331-362, Springer Verlag, 2016}.

\end{enumerate}

%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
\noindent{\bf{Journal Publications}}

\begin{enumerate}[leftmargin=0.0mm]


\item
Thomas Reynolds, Adam Procter, William L. Harrison, and Gerard Allwein.
\newblock The Mechanized Marriage of Effects and Monads with Applications to High Assurance Hardware.
\newblock {\it ACM Transactions on Embedded Computing Systems}, 2019, vol. 18, pages 1-26. 


\item
Gerard Allwein, William L. Harrison, and Thomas Reynolds.
\newblock Distributed Relation Logic.
\newblock {\it Logic and Logical Philosophy}, volume 26, number 1, March 2017, pages 19-61.


\item
Adam Procter, William L. Harrison, Ian Graves, Michela Becchi, and Gerard Allwein.
\newblock A Principled Approach to Secure Multi-Core Processor Design with ReWire
\newblock {\it ACM Transactions on Embedded Computing Systems}, volume 16, number 2, Article 33 (January 2017).


\item
Gerard Allwein, William Harrison and David Andrews.
\newblock Simulation logic.
\newblock {\it Logic and Logical Philosophy, vol. 26, no. 3}, 2014.

\item
G.~Allwein, Y.~Yang, and W.~L. Harrison.
\newblock Qualitative decision theory via channel theory.
\newblock {\em Logic and Logical Philosophy}, Volume 20, Number 1-2 (2011), pages 81--110.

\item
W.~L. Harrison and J.~Hook.
\newblock Achieving information flow security through monadic control of
  effects.
\newblock {\em Journal of  Computer Security}, 17:599--653, October 2009.

\item
X.~Z. Fu, H.~Wang, W.~L. Harrison, and R.~Harrison.
\newblock {RNA} pseudoknot prediction using term rewriting.
\newblock {\em International Journal of Data Mining and Bioinformatics}, 2(1):78-93, February 2008.

\item
W.~L. Harrison and R.~B. Kieburtz.
\newblock The logic of demand in {H}askell.
\newblock {\em Journal of Functional Programming}, 15(6):837--891, 2005.


\item
W.~L. Harrison.
\newblock Cheap (but functional) threads.
\newblock 44 pages. Accepted for publication in: {\em Higher-Order Symbolic Computation}. 

\end{enumerate}




%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
\noindent{{\bf Under Submission}}

\begin{enumerate}[leftmargin=0.0mm]


\item
Gerard Allwein, William Harrison and Thomas Reynolds.
\newblock Channel Theory and Information Flow.
\newblock {\it Journal of Applied Non-classical Logic}, 2017.


\end{enumerate}



%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
\noindent{{\bf Peer-reviewed Conference Publications}}

\begin{enumerate}[leftmargin=0.0mm]

\item 
William L. Harrison and Gerard Allwein.
\newblock Verifiable Security Templates for Hardware.
\newblock {\it Proceedings of Design, Automation, and Test in Europe (DATE 20)}. To appear.



\item 
William L. Harrison and Gerard Allwein.
\newblock Language Abstractions for Hardware-based Control-Flow Integrity Monitoring.
\newblock {\it Proceedings of the International Conference on Reconfigurable Computing and FPGAs (ReConFig18)}.


\item 
William L. Harrison and Gerard Allwein.
\newblock Semantics-directed Prototyping of Hardware Runtime Monitors.
\newblock {\it Proceedings of the 29th International Symposium on Rapid System Prototyping (RSP) (RSP18)}.
\end{enumerate}

\section{Peer-reviewed Publications (cont'd)}

\begin{enumerate}[leftmargin=0.0mm,resume]
\item 
Thomas N. Reynolds, Adam Procter, William L. Harrison, and Gerard Allwein.
\newblock A Core Calculus for Secure Hardware: Its Formal Semantics and Proof System.
\newblock {\it Proceedings of the 15th ACM-IEEE International Conference on Formal Methods and Models for System Design (MEMOCODE17)}, 2017.


\item
William L. Harrison, Adam Procter, and Gerard Allwein.
\newblock Model-driven Design \& Synthesis of the SHA-256 Cryptographic Hash Function in ReWire.
\newblock {\it Proceedings of the 27th International Symposium on Rapid System Prototyping (RSP), 2016}.

\item
William L. Harrison, Adam Procter, Ian Graves, Michela Becchi, and Gerard Allwein. 
\newblock A Programming Model for Reconfigurable Computing Based in Functional Concurrency.
\newblock {\it Proceedings of the 11th International Symposium on Reconfigurable Communication-centric Systems-on-Chip (ReCoSoC 2016)}.

\item
Ian Graves, Adam Procter, William L. Harrison, and Gerard Allwein.
\newblock Provably Correct Development of reconfigurable hardware designs via equational reasoning.
\newblock {\it Proceedings of the 2015 International Conference on
Field-Programmable Technology (FPT '15)}.

\item
Adam Procter, William L. Harrison, Ian Graves, Michela Becchi, and Gerard Allwein. 
\newblock Semantics driven hardware design, implementation, and verification with ReWire. 
\newblock {\it ACM SIGPLAN/SIGBED Conf. on Languages, Compilers, Tools and Theory for Embedded Systems (LCTES), 2015.} 

\item
Ian Graves, Adam Procter, William L. Harrison, Michela Becchi and Gerard Allwein.
\newblock Hardware Synthesis from Functional Embedded Domain-Specific Languages.
\newblock {\it Proceedings of the 2015 11th International Symposium on 
Applied Reconfigurable Computing}.


\item
Adam Procter, William L. Harrison, Ian Graves, Michela Becchi and Gerard Allwein.
\newblock Semantics-directed Machine Architecture in ReWire.
\newblock {\it Proceedings of the 2013 International Conference on Field Programmable Technology.}

\item
Robert Harrison and William L. Harrison.
\newblock Quantitative Analysis of Error Injection Covert Channels.
\newblock {\it Proceedings of the International Workshop on Quantitative Aspects in Security Assurance (QASA 2013).}

\item
   William L. Harrison, Adam Procter and Gerard Allwein.
\newblock The Confinement Problem in the Presence of Faults.
\newblock {\it Proceedings of the 2012 International Conference on Formal Engineering Methods.}
                  
\item
Chris Hathhorn, Michela Becchi, William L. Harrison and Adam Procter
\newblock Formal Semantics of Heterogeneous CUDA-C: A Modular Approach with Applications.
\newblock {\it Proceedings of the 2012 Systems Software Verification Conference.}

\item
Gerard Allwein, William L. Harrison and David Andrews.
\newblock Simulation Logic.
\newblock {\it Proceedings of the 2012 Conference on Non-Classical Logics.}

\item
 Adam Procter, William L. Harrison and Aaron Stump.
 \newblock The Design of a Practical Proof Checker for a Lazy Functional Language.
 \newblock {\it Proceedings of the 2012 Trends in Functional Programming Conference.}

\end{enumerate}

\section{Peer-reviewed Publications (cont'd)}

\begin{enumerate}[leftmargin=0.0mm,resume]
\item
W.~L. Harrison, B.~Schulz, A.~Procter, A.~Lukefahr, and G.~Allwein.
\newblock Towards semantics-directed system design and synthesis.
\newblock In {\em Proceedings of the 2011 International Conference on
  Engineering Reconfigurable Systems and Algorithms (ERSA11)}, 2011.



\item
G.~Allwein and W.~L. Harrison.
\newblock A channel theoretic account of separation security.
\newblock In {\em Proceedings of the 2011 International Conference on
  Engineering Reconfigurable Systems and Algorithms (ERSA11)}, 2011.


\item
G.~Allwein, Y.~Yang, and W.~L. Harrison.
\newblock Decision theory via channel theory.
\newblock In {\em Proceedings of the Logic in Cognitive Science Conference}. The Nicolaus Copernicus
  University Press, 2010.

\item
G.~Allwein and W.~L. Harrison.
\newblock Partially-ordered modalities.
\newblock In {\em Proceedings of the Advances in Modal Logic (AiML) Conference}, pages 1--21, 2010.

\item
W.~L. Harrison, A.~Procter, J.~Agron, G.~Kimmel, and G.~Allwein.
\newblock Model-driven engineering from modular monadic semantics:
  Implementation techniques targeting hardware and software.
\newblock In {\em DSL '09: Proc. of the IFIP TC 2 Working Conference on
  Domain-Specific Languages}, pages 20--44, 2009.



\item
W.~L. Harrison, G.~Allwein, A.~Gill, and A.~Procter.
\newblock Asynchronous exceptions as an effect.
\newblock In {\em Proceedings of the Mathematics of Program Construction
  (MPC08)}, pages 153--176, 2008.



\item
P.~S. Kariotis, A.~M. Procter, and W.~L. Harrison.
\newblock Making monads first-class with template haskell.
\newblock In {\em Proceedings of the first ACM SIGPLAN Symposium on Haskell},
  Haskell '08, pages 99--110, New York, NY, USA, 2008. ACM.

\item
W.~L. Harrison.
\newblock The essence of multitasking.
\newblock In {\em 11th International Conference on Algebraic Methodology and
  Software Technology {(AMAST 2006)}}, pages 158--172, July 2006.


\item
W.~L. Harrison.
\newblock Proof abstraction for imperative languages.
\newblock In {\em Proceedings of the 4th Asian Symposium on Programming
  Languages and Systems (APLAS06)}, pages 97--113, 2006.

\item
W.~L. Harrison and J.~Hook.
\newblock Achieving information flow security through precise control of
  effects.
\newblock In {\em 18th IEEE Computer Security Foundations Workshop (CSFW05)},
  pages 16--30, Aix-en-Provence, France, June 2005.

\item
W.~L. Harrison.
\newblock A simple semantics for polymorphic recursion.
\newblock In {\em Proceedings of the 3rd Asian Symposium on Programming
  Languages and Systems (APLAS05)}, pages 37--51, Tsukuba, Japan, November
  2005.

\item
X.~Z. Fu, H.~Wang, W.~L. Harrison, and R.~Harrison.
\newblock {RNA} pseudoknot prediction using term rewriting.
\newblock In {\em Proceedings of IEEE Fifth Symposium on Bioinformatics and
  Bioengineering (BIBE05)}, pages 169--176, Minneapolis, MN, October 2005.

\item
W.~L. Harrison and R.~W. Harrison.
\newblock Domain specific languages for cellular interactions.
\newblock In {\em Proceedings of the 26th Annual IEEE International Conference
  on Engineering in Medicine and Biology (EMBC04)}, September 2004.

\item
W.~L. Harrison, M.~Tullsen, and J.~Hook.
\newblock Domain separation by construction.
\newblock In {\em LICS03 Satellite Workshop on Foundations of Computer Security
  (FCS03)}, June 2003.
\newblock 21 pages.

\end{enumerate}

\section{Peer-reviewed Publications (cont'd)}

\begin{enumerate}[leftmargin=0.0mm,resume]
\item
W.~L. Harrison, T.~Sheard, and J.~Hook.
\newblock Fine control of demand in {Haskell}.
\newblock In {\em 6th International Conference on the Mathematics of Program
  Construction (MPC02), Dagstuhl, Germany}, volume 2386 of {\em Lecture Notes in Computer Science}, pages 68--93. 2002.



\item
W.~L. Harrison and R.~Kieburtz.
\newblock Pattern-driven reduction in haskell.
\newblock In {\em 2nd International Workshop on Reduction Strategies in
  Rewriting and Programming (WRS02)}, Copenhagen, Denmark, 2002.


\item
W.~L.~Harrison and T.~Sheard.
\newblock Dynamically adaptable software with metacomputations in a staged
  language.
\newblock In {\em Proceedings of the Second International Workshop on
  Semantics, Applications, and Implementation of Program Generation (SAIG)},
  volume 2196 of {\em Lecture Notes in Computer Science}, pages 163--182,
  Florence, Italy, 2001. Springer-Verlag.


\item
W.~L. Harrison and S.~Kamin.
\newblock Metacomputation-based compiler architecture.
\newblock In {\em 5th International Conference on the Mathematics of Program
  Construction, Ponte de Lima, Portugal}, volume 1837 of {\em Lecture Notes in
  Computer Science}, pages 213--229. Springer-Verlag, 2000.


\item
W.~L. Harrison and S.~N. Kamin.
\newblock Modular compilers based on monad transformers.
\newblock In {\em Proceedings of the 1998 International Conference on Computer
  Languages}, pages 122--131. IEEE Computer Society Press, 1998.


\item
W.~L. Harrison, K.~Levitt, and M.~Archer.
\newblock An {HOL} mechanization of the axiomatic semantics of a simple
  distributed programming language.
\newblock In {\em Proceedings of the International Workshop on Higher-Order
  Logic Theorem Proving and Its Applications}, pages 347--358, Leuven, Belgium,
  September 1992.

\item
W.~L. Harrison and K.~Levitt.
\newblock Mechanizing security in {HOL}.
\newblock In {\em Proceedings of the 1991 International Workshop on the {HOL}
  Theorem Proving System and its Applications}, pages 63--66, Davis,
  California, 1991. IEEE Computer Society Press.

\end{enumerate}

%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
\noindent{{\bf Dissertation and Master's Thesis}}

\begin{enumerate}[leftmargin=0.0mm]

\item
W.~L. Harrison.
\newblock {\em Modular Compilers and Their Correctness Proofs}.
\newblock PhD thesis, University of Illinois at Urbana-Champaign, 2001.

\item
W.~L. Harrison.
\newblock \emph{Mechanizing the axiomatic semantics for a programming language with
  asynchronous send and receive in {HOL}.}
\newblock Master's thesis, University of California, Davis, 1992.


\end{enumerate}

%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
\noindent{{\bf Technical Reports}}



\begin{enumerate}[leftmargin=0.0mm]

\item
Gerard Allwein and William L. Harrison.
\newblock {Distributed Logics}.
\newblock Technical Report NRL/MR/5540-14-9565, US Naval Research Laboratory, 2014. 

\item
W.~L. Harrison.
\newblock {Mechanizing the Axiomatic Semantics for a Programming Language with
  Asynchronous Send and Receive in HOL}.
\newblock Technical Report CSE-92-20, University of California at Davis, 1992.


\item
W.~Harrison, K.~Levitt, and M.~Archer.
\newblock {Towards a Verified Code Basis for a Secure Distributed Operating
  System}.
\newblock Technical Report CSE-92-19, University of California at Davis, 1992.

\end{enumerate}



%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
\section{Selected Honors, Memberships, and Service}


\begin{itemize}[leftmargin=0mm]

\item[] Program Committee member, 13th International Conference on
Mathematics of Program Construction (MPC), 2019.

\item[] Program Committee member, 2018 International Conference on Reconfigurable Computing and FPGAs (ReConFig), 2018.

\item[] Program Committee member, 30th International Conference on Computer Aided Verification (CAV), 2018.

\item[] Selected for Intel Corporation's 2017 Hardware Accelerator Research Program.

\item[] Program Chair for 
Seventh Workshop on Design, Modeling and Evaluation of Cyber Physical Systems (CyPhy'17).

\item[] Organized special session entitled \emph{The Confluence of Secure Hardware and Programming Languages} for the International Conference on 
Engineering of Reconfigurable Systems and Algorithms (ERSA 11).

\item[]  Recipient, National Science Foundation CAREER award (CyberTrust program) in 2008.

\item[] Received \emph{Certificate of Appreciation} from the University of Missouri College of Engineering Graduating Seniors on December 11, 2009 for teaching excellence.

\item[] Member of ACM and IEEE.

\item[] Lead successful effort to earn the University of Missouri accreditation as a National Security Agency Center of Academic Excellence in 2007. 

\item[] Invited participant to the NSF High-Confidence Software
  Platforms for Cyber-Physical Systems (HCSP-CPS) Workshop, November
  30-December 1, 2006 in Alexandria, Virginia.

\item[] Summer Faculty Fellow to the 2006 Office of Naval Research/ASEE
  Summer Faculty Research Program. Research performed in the Software
  Engineering Section of the Naval Research Laboratory's Center for
  High Assurance Computer Systems in Washington, DC. 

\item[]  Member of the program committees for the {\em Colloquium for Information Systems Security Education} (CISSE 2011, 2012), {\em ACM Symposium on the Implementation of Functional Languages} (IFL11), {\em ACM SIGPLAN 2008
    Haskell Symposium} (Haskell08), the {\em 7th International
Conference on the Mathematics of Program Construction} (MPC06).

\item[] Reviewer for the {\em Journal of Computer Security} (JCS), the {\em Journal of Functional Programming} (JFP),
the {\em ACM Transactions on Programming Languages and Systems} (TOPLAS),
the {\em Theoretical Computer Science} (TCS),
the {\em Journal of Software Testing, Verification and Reliability},
the {\em ACM Journal of Experimental Algorithmics} (JEA), and the {\em American
Medical Informatics Association Symposium 2005} (AMIA 2005). 


\item[] Received \emph{Big Twelve Faculty Fellowship}, University of
  Missouri, Columbia; visited University of Kansas System Level Design (SLDG)
  and Hybrid Threads groups.


\item[] University of Missouri nominee for 2005 {\em Microsoft New Faculty Fellowship} for Bioinformatics research.

\item[] Frequent invitations to serve and participation (usually once or twice per year)  on National Science Foundation review panels.
\end{itemize}

%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
\section{Selected Honors, Memberships, and Service (cont'd)}

\begin{itemize}[leftmargin=0.0mm]

\item[] Chaired recruiting committee that ultimately resulted in the hiring of Drs. Rohit Chadha and Prasad Calyam in the MU Computer Science department. 


\item[] Currently chairing recruiting committee for the area of ``High Assurance Cyber Physical Systems'' in the MU Computer Science department. Expect to hire 5 faculty.

\end{itemize}

%%%%%%%%%%%%
%%%%%%%%%%%%
%%%%%%%%%%%%
%%%%%%%%%%%%
\section{Invited Talks and Conference Presentations}

\begin{itemize}[leftmargin=0mm]

\item[]{\it Semantics-directed Prototyping of Hardware Runtime Monitors}. The 29th International Symposium on Rapid System Prototyping (RSP), October 2018.

\item[]{\it Why Functional Hardware Description Matters.}
Oak Ridge National Laboratory, Oak Ridge TN, 3/13/2017.


\item[]{\it Model-driven Design \& Synthesis of the SHA-256 Cryptographic Hash Function in ReWire.} The 27th International Symposium on Rapid System Prototyping (RSP), 2016.

\item[]{\it A Programming Model for Reconfigurable Computing Based in Functional Concurrency.} The 11th International Symposium on Reconfigurable Communication-centric Systems-on-Chip (ReCoSoC 2016).

\item[]{\it Provably Correct Development of reconfigurable hardware designs via equational reasoning.} The 2015 International Conference on Field-Programmable Technology (FPT ?15).

\item[]{\it High Assurance Hardware with ReWire: Just Say No! to Semantic Archaeology.}
The Technical Cooperation Program (TTCP) workshop, Defence Science \& Technology Organization (DSTO), Adelaide Australia, 5/18/2015.

\item[]{\it High Assurance Hardware with ReWire: Just Say No! to Semantic Archaeology.}
High Confidence Software and Systems (HCSS) NSA workshop, Annapolis MD, 5/6/2015.

\item[]{\it High Assurance Hardware with ReWire: Just Say No! to Semantic Archaeology.}
Oak Ridge National Laboratory, Oak Ridge TN, 3/3/2015.

\item[]{\it The Confinement Problem in the Presence of Faults.} Proceedings of the 2012 International Conference on Formal Engineering Methods.

\item[]{\it Towards semantics-directed system design and synthesis.}
International Conference on
  Engineering Reconfigurable Systems and Algorithms (ERSA), 7/19/2011.

\item[]{\it Understanding Security Flows in the Many Core Era.}
National Security Agency, Information Assurance Directorate, 
10/14/2010, Sponsor: Brad Martin.

\item[]{\it An Academic Response to National Science and Technology Challenges.}
Department of Defense Intelligence Information Systems (DoDIIS) Worldwide Conference, 5/26/2010.

\item[]{\it Model-driven Synthesis of High Assurance Secure Systems.} University of Iowa, 10/23/09, Sponsor: Professor Aaron Stump.

\item[]{\it Model-driven Synthesis of High Assurance Secure Systems.} Galois, Inc., 5/20/08, Sponsor: John Launchbury.
\end{itemize}

%%%%%%%%%%%%
%%%%%%%%%%%%
%%%%%%%%%%%%
%%%%%%%%%%%%
\section{Invited Talks and Conference Presentations (cont'd)}

\begin{itemize}[leftmargin=0mm]

\item[]{\it Compiling for Security.} Missouri Institute of Technology (formerly University of Missouri, Rolla), 4/28/08, Sponsor: Professor Bruce McMillen.

\item[]{\it Proof Abstraction for Imperative Languages.} The 4th Asian Symposium on Programming Languages and Systems (APLAS06), Sydney, Australia, 11/8/2006. 

\item[]{\it The Essence of Multitasking.} The 11th International Conference on Algebraic Methodology and Software Technology (AMAST06), Kuuresaare, Estonia, 7/5/06.

\item[]{\it Domain-specific Languages for Cellular Interactions.} University of Kansas, 4/29/05, Sponsor: Professor Perry Alexander. 

\item[]{\it A Simple Semantics for Polymorphic Recursion.}, Proceedings of the 3rd Asian Symposium on Programming Languages and Systems (APLAS05), Tsukuba, Japan, 11/3/2005.

\item[]{\it Achieving Information Flow Security Through Precise Control of Effects.} The 18th IEEE Computer Security Foundations Workshop (CSFW05), Aix-en-Provence, France, 7/20/05.

\item[]{\it Information-flow Security \& Monadic Effects.}
University of Illinois at Urbana-Champaign, 4/18/2005, Sponsor:
Professor Jos\'{e} Meseguer.

\item[]{\it Domain-specific Languages for Cellular Interactions.} The 26th Annual IEEE International Conference on Engineering in Medicine and Biology, San Francisco, California, 9/3/04.

\item[]{\it Domain-specific Languages for Biology.} Georgia State
  University, 5/26/2004, Sponsor: Professor Yi Pan.

\item[]{\it Domain Separation by Construction.} LICS03 Satellite Workshop on Foundations of Computer Security (FCS03), Ottawa, Canada, 6/26/03. 

\item[]{\it Prospects for Modular Compilation.}
Rice University, 12/11/2002, Sponsor: Professor Walid Taha.

\item[]{\it Domain-specific Languages for Compilation.}
University of Alabama, 11/22/2002, Sponsor: Professor Joel Jones.

\item[]{\it Pattern-driven Reduction in Haskell.} Second International Workshop on Reduction Strategies in Rewriting and Programming, Copenhagen, Denmark, 7/21/02.

\item[]{\emph{Fine Control of Demand in Haskell.}} The Sixth International Conference on the Mathematics of Program Construction (MPC02), Dagstuhl, Germany, 7/8/02. 

\item[]{\it Dynamically Adaptable Software with Metacomputations in a Staged Language.} The Second Workshop on the Semantics, Applications and Implementation of Program Generation (SAIG01), Florence, Italy, 9/6/01. 

\item[]{\it Metacomputation-based Compiler Architecture.} The Fifth International Conference on the Mathematics of Program Construction (MPC00), Ponte de Lima, Portugal. 7/5/00. 

\item[]{\it Modular Compilers Based on Monad Transformers.} The IEEE International Conference on Computer Languages (ICCL98), Chicago, Illinois. 5/16/98.

\end{itemize}


%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
\section{Students \& Postdocs Supervised}

\noindent{\bf Postdoctoral Researchers Supervised}

\begin{enumerate}[leftmargin=0.0mm]
\item Adam Procter. 1/2015-5/2016.
\item Soumya Sanyal. 9/2013-9/2015.
\end{enumerate}

\noindent{\bf Graduated Ph.D Students}

\begin{enumerate}[leftmargin=0.0mm]
\item Adam Procter. GAANN fellow. Graduated: 12/2014.\\
\newblock Dissertation: \emph{Semantics-directed Design and Implementation of High Assurance Hardware}.

\item Ian Graves. Graduated: 12/2015.\\
\newblock Dissertation: \emph{Device-level Composition in ReWire}.


\item Christopher Hathhorn. GAANN Fellow. Graduated: 12/2017.\\
\newblock Dissertation: \emph{Defining the Undefinedness of C11: Practical Semantics-based Program Analysis}.


\end{enumerate}


\noindent{\bf Current Ph.D Students}

\begin{enumerate}[leftmargin=0.0mm]

\item Thomas Reynolds. Started Fall semester 2014.

\item Qianli Zhang. Started Fall semester 2016.

\item Trevor Bajkowski. Started Fall semester 2018.

\item Matthew Deardorff. Started Fall semester 2018.

\end{enumerate}

%\subsection*{\it Current MS Student}
%
%\begin{hangingdesc}{}
%
%\end{hangingdesc}

\noindent{\bf Graduated MS Students}

\begin{enumerate}[leftmargin=0.0mm]
\item Daniel Dunn. Thesis: Penetration Testing FOSCAM IP Cameras. Graduated: 5/2018.
\item Zolbayar Magsar. Graduated: 5/2016.
\item Richard Wallen. Graduated: 12/2015.
\item Mohammed Alharbi. Graduated: 5/2013.
\item Jared Kvanvig. Thesis: Compiler Infrastructure for the Cheap Threads Compiler. Graduated: 12/2009.
\item Ajay Nagar.  Non-thesis. Graduated: 5/2009.
\item Megha Rao. Thesis: Physical Security in a Nuclear Environment. Graduated: 12/2008.
\item Pericles S. Kariotis. Thesis: Making Monads First-class Using Template Haskell. Graduated: 12/2008.
\end{enumerate}


\newpage
%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
\section{References}

\begin{minipage}[t]{3.1in}
\begin{flushleft}
Professor David Andrews\\
Dept. of Computer Science Engineering \\
University of Arkansas\\ 
Fayetteville, Arkansas 72701 \\
Phone: (479) 575-4394 \\
Email: dandrews@uark.edu
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{3.1in}
\begin{flushleft}
Stanley Chincheck\\
Director, Center for High Confidence Systems\\
US Naval Research Laboratory\\ 
Washington, DC  \\
Phone:  (202) 767-2932 \\
Email: stanley.chincheck@nrl.navy.mil
\end{flushleft}
\end{minipage}
\vspace{3ex}

\begin{minipage}[t]{3.1in}
\begin{flushleft}
Dr. Gerard Allwein\\
Center for High Confidence Systems\\
Formal Methods Section (5543)\\
US Naval Research Laboratory\\ 
Washington, DC  \\
Phone: (202) 404-3748 \\
Email: gerard.allwein@nrl.navy.mil
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{3.1in}
\begin{flushleft}
Professor Samuel Kamin (emeritus)\\
Department of Computer Science\\
The University of Illinois at Urbana-Champaign\\
Urbana, IL 61801. USA\\
Phone: (217) 390-7505\\
Email: kamin@uiuc.edu
\end{flushleft}
\end{minipage}

\vspace{3ex}


\begin{minipage}[t]{3.1in}
\begin{flushleft}
Professor James Hook\\
Associate Dean,
Maseeh College of Engineering and Computer Science\\
%Professor of Computer Science Department \\
Portland State University \\
Portland, Oregon 97207-0751\\
Phone: (503) 725-5540 \\
Email: hook@cs.pdx.edu
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{3.1in}
\begin{flushleft}
Professor Michela Becchi\\
Dept. of Electrical and Computer Engineering\\
North Carolina State University\\
Phone: (573) 823-5537\\
Email: mbecchi@ncsu.edu
\end{flushleft}
\end{minipage}


\end{document}
