
%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt]{article} % Default document font size

%----------------------------------------------------------------------------------------
%	REQUIRED PACKAGES AND MISC CONFIGURATIONS
%----------------------------------------------------------------------------------------

\usepackage{graphicx} % Required for including images
\usepackage{fancyhdr}
\usepackage{enumitem}

\setlength{\parindent}{0pt} % Stop paragraph indentation

%----------------------------------------------------------------------------------------
%	MARGINS
%----------------------------------------------------------------------------------------

\usepackage{geometry} % Required for adjusting page dimensions and margins

\geometry{
	paper=letterpaper, % Paper size, change to letterpaper for US letter size
	top=3.25cm, % Top margin
	bottom=4cm, % Bottom margin
	left=3.5cm, % Left margin
	right=3.5cm, % Right margin
	headheight=0.75cm, % Header height
	footskip=1cm, % Space from the bottom margin to the baseline of the footer
	headsep=0.75cm, % Space from the top margin to the baseline of the header
	%showframe, % Uncomment to show how the type block is set on the page
}

%----------------------------------------------------------------------------------------
%	FONTS
%----------------------------------------------------------------------------------------

\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters

\usepackage[semibold]{ebgaramond} % Use the EB Garamond font with a reduced bold weight

%----------------------------------------------------------------------------------------
%	SECTION STYLING
%----------------------------------------------------------------------------------------

\usepackage{sectsty} % Allows changing the font options for sections in a document

%\sectionfont{\fontsize{13.5pt}{18pt}\selectfont} % Set font options for sections
\sectionfont{\fontsize{15pt}{18pt}\selectfont} % Set font options for sections
\subsectionfont{\bfseries\scshape\normalsize} % Set font options for subsections
\subsubsectionfont{\mdseries\upshape\bfseries\normalsize} % Set font options for subsubsections

%----------------------------------------------------------------------------------------
%	MARGIN YEARS
%----------------------------------------------------------------------------------------

\usepackage{marginnote} % Required to output text in the margin

\newcommand{\years}[1]{\marginnote{\scriptsize #1}} % New command for adding years to the margin
\renewcommand*{\raggedleftmarginnote}{} % Left-align the years in the margin
\setlength{\marginparsep}{-10pt} % Move the margin content closer to the text
\reversemarginpar % Margin text to be output into the left margin instead of the default right margin

%----------------------------------------------------------------------------------------
%	COLOURS
%----------------------------------------------------------------------------------------

\usepackage[usenames, dvipsnames]{xcolor} % Required for specifying colours by name

%----------------------------------------------------------------------------------------
%	LINKS
%----------------------------------------------------------------------------------------

\usepackage[bookmarks, colorlinks, breaklinks]{hyperref} % Required for links

% Set link colours
\hypersetup{
	linkcolor=blue,
	citecolor=blue,
	filecolor=black,
	urlcolor=MidnightBlue
}

% Set PDF meta-information
\hypersetup{
	pdftitle={William L. Harrison - Curriculum vitae},
	pdfauthor={William L. Harrison}
}

%----------------------------------------------------------------------------------------

\begin{document}
%----------------------------------------------------------------------------------------
%	CONTACT AND GENERAL INFORMATION
%----------------------------------------------------------------------------------------

%\begin{tabular}{rl}
%    \textsc{Address:}   & 3033 Kenilworth Lane, Knoxville TN 37917 \\
%    \textsc{Phone:}     & 573 268-7402\\
%    \textsc{Email:}     & \href{mailto:william.lawrence.harrison@gmail.com}{william.lawrence.harrison@gmail.com}\\
%    \textsc{Web:}       & \href{https://harrisonwl.github.io}{https://harrisonwl.github.io}
%\end{tabular}

{\LARGE\bfseries William L. Harrison, Ph.D} % Name
%\bigskip\bigskip
\medskip % Whitespace

%%%%%%%%%%%
%\section*{Contact Information}

\textsc{Address:} 81 East High Point Lane, Columbia, MO 65203
\\
\textsc{Phone:} 573-268-7402
\\ 
\textsc{Email:} \href{mailto:william.lawrence.harrison@gmail.com}{william.lawrence.harrison@gmail.com}
\\
\textsc{url}: \href{https://harrisonwl.github.io}{https://harrisonwl.github.io}
 % Academic/personal website

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section*{Education}


\begin{tabular}{  l   l }
\years{2001}\textsc{PhD} in Computer Science & \textbf{University of Illinois at Urbana-Champaign}  
    \\ 
%\multicolumn{2}{l}{Dissertation: ``Modular Compilers and Their Correctness Proofs.''} 
%\\
%\multicolumn{2}{l}{Advisor: Samuel Kamin} 
%\\
\years{1992}\textsc{MS} in Computer Science & \textbf{University of California, Davis}
     \\ 
%\multicolumn{2}{l}{Thesis: ``Mechanizing the Axiomatic Semantics for a Programming 
%Language with} 
%\\
%\multicolumn{2}{l}{Asynchronous Send and Receive in HOL.''}
%\\
%\multicolumn{2}{l}{Thesis Advisor: Karl Levitt}
%\\
\years{1986}\textsc{BA} in Mathematics   & \textbf{University of California, Berkeley}
\end{tabular}

%------------------------------------------------
%
%\section*{Current position}
%
%\emph{Senior Cybersecurity Scientist}, Oak Ridge National Laboratory, Oak Ridge, TN % Current or most recent employment position

%------------------------------------------------

\section*{Research Interests}

Reconfigurable computing and high-level synthesis from functional languages.
Computer security and, in particular, 
language-based methods in security; Trustworthy computing for cyber physical systems.
All aspects of programming language
design and implementation; Software Formal Methods for Zero-Trust Computing.
 


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\section*{Academic and Professional Appointments}

\years{9/24-}\textsc{Senior Formal Methods Scientist/Directorate Fellow}, Idaho National Laboratory, Idaho Falls, Idaho. Fully remote.
\\
\years{7/21-8/24}\textsc{Senior Principal Research Scientist}, High Assurance Systems Group, Two Six Technologies, Inc., Arlington VA
\\
\years{9/23--}\textsc{Critical Infrastructure Faculty Researcher}, Idaho National Laboratory (DOE), Idaho Falls, ID
\\
\years{8/19-6/21}\textsc{Senior Cybersecurity Scientist}, Cyber Security Research Group (CYR), Oak Ridge National Laboratory, Oak Ridge TN
\\
\years{9/03-7/19}\textsc{Associate Professor}, Department of Computer
Science,
University of Missouri at Columbia. Promotion and tenure 5/26/2009
\\
\years{9/17-12/17}\textsc{Visiting Scientist}, Oak Ridge National Laboratory
\\
\years{8/13-7/14}\textsc{Visiting Scientist}, National Security Agency
\\
\years{4/11-7/19}\textsc{Director}, The Center for High Assurance Computing at the University of Missouri
\\
\years{9/10-8/13}\textsc{Research Consultant}, Pro-telligent, Inc. 
Arlington, VA
\\
\years{6/00-8/03}\textsc{Senior Research Associate \& Adjunct Professor}, Computer
Science Dept.,
Oregon Graduate Institute, Beaverton OR
\\
\years{2000}\textsc{Senior Compiler Engineer (consultant)}, Reservoir
Laboratories, Portland, Oregon.
\\
\years{8/99-5/00}\textsc{Visiting Lecturer}, Department of Computer Science,
	Indiana University
\\
\years{Spr 1999}\textsc{Visiting Lecturer}, Department of Computer Science,
	  UIUC


%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
\section*{Funding History}

This section summarizes my experience obtaining funding and performing on funded research project. 
In 2008, I received a CAREER award from the National Science Foundation.

%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
\subsection*{DARPA Proposals \& Experience at Two Six Technologies}

While at Two Six Technologies, I wrote successful Defense Advanced Research Projects Agency (DARPA) proposals as part of a team, and performed in the roles of Principal Investigator and Research Scientist. This list only includes unclassified roles. I have also not included the numerous DARPA proposals I contributed to significantly while at Two Six.
\\
\\
%{\bf Agency:} Defense Advanced Research Projects Agency (DARPA).
%\\
{\bf Program:} \href{https://www.darpa.mil/news-events/2021-09-22}{HARDEN: Hardening Development Toolchains against Emergent Execution}.
%\\
%{\bf Title:} CATERPIE (Computerized Analysis for Trusted Execution Reasoning of Prioritized Interconnected Executables).
\\
{\bf Start Date:} October 2022.
\\
%{\bf Budget/Duration:} 1.5 FTE (full-time employee) for four years.
%\\
{\bf Role:} Proposal writer and Principal Investigator.
\\
\\
{\bf Program:} \href{https://www.darpa.mil/research/programs/data-protection-in-virtual-environments}{DPRIVE: Data Protection In Virtual Environments}.
\\
{\bf Roles:} Research Scientist (7/21-7/23) and Principal Investigator (8/23-8/24). My functional hardware language \href{https://github.com/twosixlabs/ReWire}{ReWire} is a central, critical technology in Two Six's DPRIVE research.

%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
\subsection*{Laboratory Directed Research and Development (LDRD) Projects}

{\bf Agency:} US Department of Energy/Idaho National Laboratory.
\\
{\bf Title:} Physical Modeling for Assured Cyber Resilience (LDRD).
\\
{\bf Amount:} \$1,510,000.
\\
{\bf Period:}   October 2024  --  September 2027.
\\
{\bf Role:}    Principal investigator.
\\

{\bf Agency:} US Department of Energy/Oak Ridge National Laboratory.
\\
{\bf Title:} Expanding the High-Level Synthesis Trust Zone (LDRD SEED).
\\
{\bf Amount:} \$190,000.
\\
{\bf Period:}   October 2020  --  September 2021.
\\
{\bf Role:}    Sole Principal investigator (until 7/21 when I joined Two Six Technologies).

%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%% 
\subsection*{Funded Research at the University of Missouri} 

Total funding during this period is $\$4,718,292$.
 
{\bf Agency:} US Naval Research Laboratory.
\\
{\bf Title:} Mechanizing the Metatheory of the ReWire Language with Applications.
\\
{\bf Amount:} \$720,000.
\\
{\bf Period:}   May 2016  --  August 2019.
\\
{\bf Role:}    Sole  Principal investigator.
\\
{\bf Agency:} US Naval Research Laboratory.
\\
{\bf Title:} Integrated Formal Methods for Secure FPGA Development.
\\
{\bf Amount:} \$300,000.
\\
{\bf Period:}   January 2019  --  December 2021.
\\
{\bf Role:}    Sole  Principal investigator.
\\


{\bf Agency:} US Naval Research Laboratory.
\\
{\bf Title:} Type-Based Analysis of Security Flows in ReWire Circuit Specifications.
\\
{\bf Amount:} \$99,999.
\\
{\bf Period:}   October 2014  --  October 2015.
\\
{\bf Role:}     Sole Principal investigator.
\\

{\bf Agency:} National Security Agency.\\
{\bf Title:} Inter-agency Personnel Agreement.\\
{\bf Amount:} \$144,190.00 \\
{\bf Period:} August 2013 -- August 2014.
\\


{\bf Agency:} Department of Defense, Federal Voting Assistance Program (FVAP).
\\
{\bf Title:} Secure Ballot Delivery to UOCAVA Voters (Uniformed, Overseas, Citizens Absentee Voters). 
\\
{\bf Amount:} \$550,000.
\\
{\bf Period:} May 1, 2012 -- April 30, 2015.
\\
{\bf Role:} Collaborative research with Dr. Dale Musser of MU's Information Technology Program and Dr. Keith Politte of MU's Reynolds School of Journalism. 
\\

%\thispagestyle{fancyplain}
%\fancyhf{}
%\renewcommand{\headrulewidth}{0pt}
%\chead{ \fancyplain{}{{\bf\large{Funding History (cont'd)} }}}
%\cfoot{ \fancyplain{}{\thepage} }


{\bf Agency:} Department of Education.
 ~\\
{\bf Title:} Graduate Assistance in Areas of National Need (GAANN) Fellowships.
\\
{\bf Amount:} \$240,000.
\\
{\bf Period:} September 1, 2011 -- May 15, 2015.
\\
{\bf Role:} Co-Investigator. Two of my Ph.D students (Adam Procter and Christopher Hathhorn) were GAANN fellows. 
\\

{\bf Agency:} National Science Foundation.
\\
{\bf Title:} CAREER: Automated Synthesis of High Assurance Security Kernels.
\\
{\bf Amount:} \$450,000.
\\
{\bf Period:}   June 1, 2008  --  May 31, 2013.
\\
{\bf Role:}      Sole Principal Investigator.
\\

{\bf Agency:} Office of the Asst. Secretary of Defense for Research and Development (ASD(R\&E)).
\\
{\bf Title:} Understanding Security Flows in the Many Core Era.
\\
{\bf Amount:} \$1,370,000.
\\
{\bf Period:}   January 2012  --  July 2015.
\\
{\bf Role:}      Principal Investigator. Collaborative Research with Dr. David Andrews (University of Arkansas) and Dr. Gerard Allwein (NRL).
\\

{\bf Agency:} US Naval Research Laboratory.
\\
{\bf Title:} MILS Hardware and Its Formal Methods-based Security.
\\
{\bf Amount:} \$810,000.
\\
{\bf Period:}   April 2008  --  April 2011.
\\
{\bf Role:}      Principal Investigator. Collaborative Research with Dr. David Andrews (University of Arkansas) and Dr. Gerard Allwein (NRL).
\\


{\bf Agency:} Department of Defense through OHSU/OGI.
\\
{\bf Title:} System Information Assurance II
\\
{\bf Amount:} \$31,703 
\\
{\bf Period:}   July 1, 2004  --  July 31, 2006
\\
{\bf Role:}      Principal Investigator


{\bf Agency:} University of Missouri-Columbia Research Council.
\\
{\bf Title:} Big Twelve Faculty Fellowship
\\
{\bf Amount:} \$2,400
\\
{\bf Period:}   June 1, 2005  --  August 31, 2005 
\\
{\bf Role:}      Sole Principal Investigator
\\

%\thispagestyle{fancyplain}
%\fancyhf{}
%\renewcommand{\headrulewidth}{0pt}
%\chead{ \fancyplain{}{{\bf\large{ Funding History (cont'd)} }}}
%\cfoot{ \fancyplain{}{\thepage} }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Peer-reviewed Publications}

%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
\subsection*{Book Chapters}

Gerard Allwein and William L. Harrison.
\newblock Distributed Relation Algebra.
\newblock {\it Relevance Logics and other Tools for Reasoning. Essays in Honor of J. Michael Dunn, Book Chapter, pages 1-30, Springer Verlag, 2022}.
\\

Gerard Allwein and William L. Harrison.
\newblock Distributed Modal Logic.
\newblock {\it J. Michael Dunn on Information Based Logics, Book Chapter, pages 331-362, Springer Verlag, 2016}.

%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
\subsection*{Journal Publications}


Thomas Reynolds, Adam Procter, William L. Harrison, and Gerard Allwein.
\newblock The Mechanized Marriage of Effects and Monads with Applications to High Assurance Hardware.
\newblock {\it ACM Transactions on Embedded Computing Systems}, 2019, vol. 18, pages 1-26. 
\\


Gerard Allwein, William L. Harrison, and Thomas Reynolds.
\newblock Distributed Relation Logic.
\newblock {\it Logic and Logical Philosophy}, volume 26, number 1, March 2017, pages 19-61.
\\


Adam Procter, William L. Harrison, Ian Graves, Michela Becchi, and Gerard Allwein.
\newblock A Principled Approach to Secure Multi-Core Processor Design with ReWire
\newblock {\it ACM Transactions on Embedded Computing Systems}, volume 16, number 2, Article 33 (January 2017).
\\

Gerard Allwein, William Harrison and David Andrews.
\newblock Simulation logic.
\newblock {\it Logic and Logical Philosophy, vol. 26, no. 3}, 2014.
\\

G.~Allwein, Y.~Yang, and W.~L. Harrison.
\newblock Qualitative decision theory via channel theory.
\newblock {\em Logic and Logical Philosophy}, Volume 20, Number 1-2 (2011), pages 81--110.
\\


W.~L. Harrison and J.~Hook.
\newblock Achieving information flow security through monadic control of
  effects.
\newblock {\em Journal of  Computer Security}, 17:599--653, October 2009.
\\

X.~Z. Fu, H.~Wang, W.~L. Harrison, and R.~Harrison.
\newblock {RNA} pseudoknot prediction using term rewriting.
\newblock {\em International Journal of Data Mining and Bioinformatics}, 2(1):78-93, February 2008.
\\


W.~L. Harrison and R.~B. Kieburtz.
\newblock The logic of demand in {H}askell.
\newblock {\em Journal of Functional Programming}, 15(6):837--891, 2005.
\\


W.~L. Harrison.
\newblock Cheap (but functional) threads.
\newblock 44 pages. Accepted for publication in: {\em Higher-Order Symbolic Computation}. 

%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
\subsection*{Conference Publications}

\begin{enumerate}[leftmargin=0.0mm]

\item Arthur Amorim, Max Taylor, Gary T. Leavens, William Harrison, Lance Joneckis, and Trevor Kann.
\newblock Enforcing MAVLink Safety \& Security Properties via Refined Multiparty Session Types.
\newblock To appear: \emph{Proceedings of the 2025 NASA Formal Methods Symposium (NFM25).}

\item Yakir Forman and William L.  Harrison.
\newblock Temporal Staging for Correct-by-Construction Cryptographic Hardware.
\newblock \emph{Proceedings of the 2024 Rapid Systems Prototyping Symposium (RSP24).}


\item William L.  Harrison, Ian Blumenfeld, Eric Bond, Chris Hathhorn, Paul Li, May Torrence, and Jared Ziegler.
\newblock Formalized High Level Synthesis with Applications to Cryptographic Hardware.
\newblock \emph{Proceedings of the 2023 NASA Formal Methods Symposium (NFM23).}

\item William L.  Harrison, Chris Hathhorn, and Gerard Allwein.
\newblock A Mechanized Semantic Metalanguage for High Level Synthesis.  
\newblock \emph{Proceedings of 23rd International Symposium on Principles and Practice of Declarative Programming (PPDP 2021).}

%\item
%William Harrison, Chris Hathhorn, and Gerard Allwein.
%\newblock High Assurance is FIRRTL Ground.
%\newblock Submitted to {\it International Conference on Interactive Theorem Proving (ITP 2021)}.

\item
Thomas Reynolds, William L. Harrison, Rohit Chadha, and Gerard Allwein.
\newblock Strongly Bounded Termination with Applications to Security and Hardware Synthesis.
\newblock {\it Proceedings of ACM Workshop on Type Driven Development (TyDe 2020)}.

\item 
William L. Harrison and Gerard Allwein.
\newblock Verifiable Security Templates for Hardware.
\newblock {\it Proceedings of Design, Automation, and Test in Europe (DATE 20)}. 

\item 
William L. Harrison and Gerard Allwein.
\newblock Language Abstractions for Hardware-based Control-Flow Integrity Monitoring.
\newblock {\it Proceedings of the International Conference on Reconfigurable Computing and FPGAs (ReConFig18)}.

\item 
William L. Harrison and Gerard Allwein.
\newblock Semantics-directed Prototyping of Hardware Runtime Monitors.
\newblock {\it Proceedings of the 29th International Symposium on Rapid System Prototyping (RSP) (RSP18)}.

\item 
Thomas N. Reynolds, Adam Procter, William L. Harrison, and Gerard Allwein.
\newblock A Core Calculus for Secure Hardware: Its Formal Semantics and Proof System.
\newblock {\it Proceedings of the 15th ACM-IEEE International Conference on Formal Methods and Models for System Design (MEMOCODE17)}, 2017.


\item
William L. Harrison, Adam Procter, and Gerard Allwein.
\newblock Model-driven Design \& Synthesis of the SHA-256 Cryptographic Hash Function in ReWire.
\newblock {\it Proceedings of the 27th International Symposium on Rapid System Prototyping (RSP), 2016}.


%\thispagestyle{fancyplain}
%\fancyhf{}
%\renewcommand{\headrulewidth}{0pt}
%\chead{ \fancyplain{}{{\bf{\large{Peer-reviewed Publications (cont'd)} }}}}
%\cfoot{ \fancyplain{}{\thepage} }


\item
William L. Harrison, Adam Procter, Ian Graves, Michela Becchi, and Gerard Allwein. 
\newblock A Programming Model for Reconfigurable Computing Based in Functional Concurrency.
\newblock {\it Proceedings of the 11th International Symposium on Reconfigurable Communication-centric Systems-on-Chip (ReCoSoC 2016)}.

\item
Ian Graves, Adam Procter, William L. Harrison, and Gerard Allwein.
\newblock Provably Correct Development of reconfigurable hardware designs via equational reasoning.
\newblock {\it Proceedings of the 2015 International Conference on
Field-Programmable Technology (FPT '15)}.

\item
Adam Procter, William L. Harrison, Ian Graves, Michela Becchi, and Gerard Allwein. 
\newblock Semantics driven hardware design, implementation, and verification with ReWire. 
\newblock {\it ACM SIGPLAN/SIGBED Conf. on Languages, Compilers, Tools and Theory for Embedded Systems (LCTES), 2015.} 

\item
Ian Graves, Adam Procter, William L. Harrison, Michela Becchi and Gerard Allwein.
\newblock Hardware Synthesis from Functional Embedded Domain-Specific Languages.
\newblock {\it Proceedings of the 2015 11th International Symposium on 
Applied Reconfigurable Computing}.


\item
Adam Procter, William L. Harrison, Ian Graves, Michela Becchi and Gerard Allwein.
\newblock Semantics-directed Machine Architecture in ReWire.
\newblock {\it Proceedings of the 2013 International Conference on Field Programmable Technology.}

\item
Robert Harrison and William L. Harrison.
\newblock Quantitative Analysis of Error Injection Covert Channels.
\newblock {\it Proceedings of the International Workshop on Quantitative Aspects in Security Assurance (QASA 2013).}

\item
   William L. Harrison, Adam Procter and Gerard Allwein.
\newblock The Confinement Problem in the Presence of Faults.
\newblock {\it Proceedings of the 2012 International Conference on Formal Engineering Methods.}
                  

\item
Chris Hathhorn, Michela Becchi, William L. Harrison and Adam Procter
\newblock Formal Semantics of Heterogeneous CUDA-C: A Modular Approach with Applications.
\newblock {\it Proceedings of the 2012 Systems Software Verification Conference.}

\item
Gerard Allwein, William L. Harrison and David Andrews.
\newblock Simulation Logic.
\newblock {\it Proceedings of the 2012 Conference on Non-Classical Logics.}


\item
 Adam Procter, William L. Harrison and Aaron Stump.
 \newblock The Design of a Practical Proof Checker for a Lazy Functional Language.
 \newblock {\it Proceedings of the 2012 Trends in Functional Programming Conference.}


\item
W.~L. Harrison, B.~Schulz, A.~Procter, A.~Lukefahr, and G.~Allwein.
\newblock Towards semantics-directed system design and synthesis.
\newblock In {\em Proceedings of the 2011 International Conference on
  Engineering Reconfigurable Systems and Algorithms (ERSA11)}, 2011.

\item
G.~Allwein and W.~L. Harrison.
\newblock A channel theoretic account of separation security.
\newblock In {\em Proceedings of the 2011 International Conference on
  Engineering Reconfigurable Systems and Algorithms (ERSA11)}, 2011.

%\thispagestyle{fancyplain}
%\fancyhf{}
%\renewcommand{\headrulewidth}{0pt}
%\chead{ \fancyplain{}{{\bf{\large{Peer-reviewed Publications (cont'd)} }}}}
%\cfoot{ \fancyplain{}{\thepage} }


\item
G.~Allwein, Y.~Yang, and W.~L. Harrison.
\newblock Decision theory via channel theory.
\newblock In {\em Proceedings of the Logic in Cognitive Science Conference}. The Nicolaus Copernicus
  University Press, 2010.

\item
G.~Allwein and W.~L. Harrison.
\newblock Partially-ordered modalities.
\newblock In {\em Proceedings of the Advances in Modal Logic (AiML) Conference}, pages 1--21, 2010.

\item
W.~L. Harrison, A.~Procter, J.~Agron, G.~Kimmel, and G.~Allwein.
\newblock Model-driven engineering from modular monadic semantics:
  Implementation techniques targeting hardware and software.
\newblock In {\em DSL '09: Proc. of the IFIP TC 2 Working Conference on
  Domain-Specific Languages}, pages 20--44, 2009.



\item
W.~L. Harrison, G.~Allwein, A.~Gill, and A.~Procter.
\newblock Asynchronous exceptions as an effect.
\newblock In {\em Proceedings of the Mathematics of Program Construction
  (MPC08)}, pages 153--176, 2008.



\item
P.~S. Kariotis, A.~M. Procter, and W.~L. Harrison.
\newblock Making monads first-class with template haskell.
\newblock In {\em Proceedings of the first ACM SIGPLAN Symposium on Haskell},
  Haskell '08, pages 99--110, New York, NY, USA, 2008. ACM.

\item
W.~L. Harrison.
\newblock The essence of multitasking.
\newblock In {\em 11th International Conference on Algebraic Methodology and
  Software Technology {(AMAST 2006)}}, pages 158--172, July 2006.


\item
W.~L. Harrison.
\newblock Proof abstraction for imperative languages.
\newblock In {\em Proceedings of the 4th Asian Symposium on Programming
  Languages and Systems (APLAS06)}, pages 97--113, 2006.

\item
W.~L. Harrison and J.~Hook.
\newblock Achieving information flow security through precise control of
  effects.
\newblock In {\em 18th IEEE Computer Security Foundations Workshop (CSFW05)},
  pages 16--30, Aix-en-Provence, France, June 2005.

\item
W.~L. Harrison.
\newblock A simple semantics for polymorphic recursion.
\newblock In {\em Proceedings of the 3rd Asian Symposium on Programming
  Languages and Systems (APLAS05)}, pages 37--51, Tsukuba, Japan, November
  2005.

\item
X.~Z. Fu, H.~Wang, W.~L. Harrison, and R.~Harrison.
\newblock {RNA} pseudoknot prediction using term rewriting.
\newblock In {\em Proceedings of IEEE Fifth Symposium on Bioinformatics and
  Bioengineering (BIBE05)}, pages 169--176, Minneapolis, MN, October 2005.

\item
W.~L. Harrison and R.~W. Harrison.
\newblock Domain specific languages for cellular interactions.
\newblock In {\em Proceedings of the 26th Annual IEEE International Conference
  on Engineering in Medicine and Biology (EMBC04)}, September 2004.

\item
W.~L. Harrison, M.~Tullsen, and J.~Hook.
\newblock Domain separation by construction.
\newblock In {\em LICS03 Satellite Workshop on Foundations of Computer Security
  (FCS03)}, June 2003.
\newblock 21 pages.

\item
W.~L. Harrison, T.~Sheard, and J.~Hook.
\newblock Fine control of demand in {Haskell}.
\newblock In {\em 6th International Conference on the Mathematics of Program
  Construction (MPC02), Dagstuhl, Germany}, volume 2386 of {\em Lecture Notes in Computer Science}, pages 68--93. 2002.

\item
W.~L. Harrison and R.~Kieburtz.
\newblock Pattern-driven reduction in haskell.
\newblock In {\em 2nd International Workshop on Reduction Strategies in
  Rewriting and Programming (WRS02)}, Copenhagen, Denmark, 2002.


%\thispagestyle{fancyplain}
%\fancyhf{}
%\renewcommand{\headrulewidth}{0pt}
%\chead{ \fancyplain{}{{\bf{\large{Peer-reviewed Publications (cont'd)} }}}}
%\cfoot{ \fancyplain{}{\thepage} }

\item
W.~L.~Harrison and T.~Sheard.
\newblock Dynamically adaptable software with metacomputations in a staged
  language.
\newblock In {\em Proceedings of the Second International Workshop on
  Semantics, Applications, and Implementation of Program Generation (SAIG)},
  volume 2196 of {\em Lecture Notes in Computer Science}, pages 163--182,
  Florence, Italy, 2001. Springer-Verlag.


\item
W.~L. Harrison and S.~Kamin.
\newblock Metacomputation-based compiler architecture.
\newblock In {\em 5th International Conference on the Mathematics of Program
  Construction, Ponte de Lima, Portugal}, volume 1837 of {\em Lecture Notes in
  Computer Science}, pages 213--229. Springer-Verlag, 2000.


\item
W.~L. Harrison and S.~N. Kamin.
\newblock Modular compilers based on monad transformers.
\newblock In {\em Proceedings of the 1998 International Conference on Computer
  Languages}, pages 122--131. IEEE Computer Society Press, 1998.


\item
W.~L. Harrison, K.~Levitt, and M.~Archer.
\newblock An {HOL} mechanization of the axiomatic semantics of a simple
  distributed programming language.
\newblock In {\em Proceedings of the International Workshop on Higher-Order
  Logic Theorem Proving and Its Applications}, pages 347--358, Leuven, Belgium,
  September 1992.

\item
W.~L. Harrison and K.~Levitt.
\newblock Mechanizing security in {HOL}.
\newblock In {\em Proceedings of the 1991 International Workshop on the {HOL}
  Theorem Proving System and its Applications}, pages 63--66, Davis,
  California, 1991. IEEE Computer Society Press.


%\thispagestyle{fancyplain}
%\fancyhf{}
%\renewcommand{\headrulewidth}{0pt}
%\chead{ \fancyplain{}{{\bf{\large{Peer-reviewed Publications (cont'd)} }}}}
%\cfoot{ \fancyplain{}{\thepage} }

\end{enumerate}


%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
\subsection*{Dissertation and Master's Thesis}


\begin{enumerate}[leftmargin=0.0mm]

\item
W.~L. Harrison.
\newblock {\em Modular Compilers and Their Correctness Proofs}.
\newblock PhD thesis, University of Illinois at Urbana-Champaign, 2001.

\item
W.~L. Harrison.
\newblock \emph{Mechanizing the axiomatic semantics for a programming language with
  asynchronous send and receive in {HOL}.}
\newblock Master's thesis, University of California, Davis, 1992.


\thispagestyle{fancyplain}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\chead{ \fancyplain{}{{\bf{\large{Peer-reviewed Publications (cont'd)} }}}}
\cfoot{ \fancyplain{}{\thepage} }

\end{enumerate}

%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
\subsection*{Technical Reports}



\begin{enumerate}[leftmargin=0.0mm]

\item
Gerard Allwein and William L. Harrison.
\newblock {Distributed Logics}.
\newblock Technical Report NRL/MR/5540-14-9565, US Naval Research Laboratory, 2014. 

\item
W.~L. Harrison.
\newblock {Mechanizing the Axiomatic Semantics for a Programming Language with
  Asynchronous Send and Receive in HOL}.
\newblock Technical Report CSE-92-20, University of California at Davis, 1992.


\item
W.~Harrison, K.~Levitt, and M.~Archer.
\newblock {Towards a Verified Code Basis for a Secure Distributed Operating
  System}.
\newblock Technical Report CSE-92-19, University of California at Davis, 1992.

\end{enumerate}


%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
\section*{Selected Honors, Memberships, and Service}

\begin{enumerate}[leftmargin=0mm]

\item Program Committee member, Formal Methods in Computer-Aided Design (FMCAD) in 2023 and 2024.

\item Founder, Cyber Security Center @ Mizzou (\href{https://engineering.missouri.edu/cybersecurity/}{weblink}).

\item Lead successful effort to earn the University of Missouri accreditation as a National Security Agency Center of Research Excellence in 2019. 

\item Program Committee member, 2019 International Conference on Reconfigurable Computing and FPGAs (ReConFig), 2019.

\item Program Committee member, 13th International Conference on
Mathematics of Program Construction (MPC), 2019.

\item Program Committee member, 2018 International Conference on Reconfigurable Computing and FPGAs (ReConFig), 2018.

\item Program Committee member, 30th International Conference on Computer Aided Verification (CAV), 2018.

\item Selected for Intel Corporation's 2017 Hardware Accelerator Research Program.

\item Program Chair for 
Seventh Workshop on Design, Modeling and Evaluation of Cyber Physical Systems (CyPhy'17).

\item Organized special session entitled \emph{The Confluence of Secure Hardware and Programming Languages} for the International Conference on 
Engineering of Reconfigurable Systems and Algorithms (ERSA 11).

\item  Recipient, National Science Foundation CAREER award (CyberTrust program) in 2008.

\item Received \emph{Certificate of Appreciation} from the University of Missouri College of Engineering Graduating Seniors on December 11, 2009 for teaching excellence.

\item Member of ACM and IEEE.

\item Lead successful effort to earn the University of Missouri accreditation as a National Security Agency Center of Academic Excellence in 2007. 

\item Invited participant to the NSF High-Confidence Software
  Platforms for Cyber-Physical Systems (HCSP-CPS) Workshop, November
  30-December 1, 2006 in Alexandria, Virginia.


\item Summer Faculty Fellow to the 2006 Office of Naval Research/ASEE
  Summer Faculty Research Program. Research performed in the Software
  Engineering Section of the Naval Research Laboratory's Center for
  High Assurance Computer Systems in Washington, DC. 

\item  Member of the program committees for the {\em Colloquium for Information Systems Security Education} (CISSE 2011, 2012), {\em ACM Symposium on the Implementation of Functional Languages} (IFL11), {\em ACM SIGPLAN 2008
    Haskell Symposium} (Haskell08), the {\em 7th International
Conference on the Mathematics of Program Construction} (MPC06).

\item Reviewer for the {\em Journal of Computer Security} (JCS), the {\em Journal of Functional Programming} (JFP),
the {\em ACM Transactions on Programming Languages and Systems} (TOPLAS),
the {\em Theoretical Computer Science} (TCS),
the {\em Journal of Software Testing, Verification and Reliability},
the {\em ACM Journal of Experimental Algorithmics} (JEA), and the {\em American
Medical Informatics Association Symposium 2005} (AMIA 2005). 


\item Received \emph{Big Twelve Faculty Fellowship}, University of
  Missouri, Columbia; visited University of Kansas System Level Design (SLDG)
  and Hybrid Threads groups.


%\thispagestyle{fancyplain}
%\fancyhf{}
%\renewcommand{\headrulewidth}{0pt}
%\chead{ \fancyplain{}{{\bf\large{ Selected Honors, Memberships, and Service (cont'd)} }}}
%\cfoot{ \fancyplain{}{\thepage} }


\item University of Missouri nominee for 2005 {\em Microsoft New Faculty Fellowship} for Bioinformatics research.

\item Frequent invitations to serve and participation (usually once or twice per year)  on National Science Foundation review panels.


\item Chaired recruiting committee that ultimately resulted in the hiring of Drs. Rohit Chadha and Prasad Calyam in the MU Computer Science department. 


\end{enumerate}



%----------------------------------------------------------------------------------------
%	Talks
%----------------------------------------------------------------------------------------


%%%%%%%%%%%%
%%%%%%%%%%%%
%%%%%%%%%%%%
%%%%%%%%%%%%
\section*{Invited Talks and Conference Presentations}

\begin{enumerate}[leftmargin=0mm]

\item{\it Why Functional Hardware Description Matters}. Sandia Laboratory, Ratish Punnoose (host). 12/20/24.

\item{\it Why Functional Hardware Description Matters}. SRI International. 11/30/24.

\item{\it Why Functional Hardware Description Matters}. Galois. 7/5/23.



\item{\it A Mechanized Semantic Metalanguage for High Level Synthesis}. 23rd International Symposium on Principles and Practice of Declarative Programming (PPDP 2021), September 8, 2021. \href{https://www.youtube.com/watch?v=fZYWlE5XR_Y}{Video}.

\item{\it Strongly Bounded Termination with Applications to Security and Hardware Synthesis}. ACM Workshop on Type Driven Development (TyDe 2020), August 22, 2020. \href{https://www.youtube.com/watch?v=IQ2Xp4mWBIk}{Video}.

\item{\it Verifiable Security Templates for Hardware}. 2020 Design, Automation, and Test Europe Conference, March 11, 2020. \href{https://www.youtube.com/watch?v=EOCoqE7PZNs}{Video}.

\item{\it Language Abstractions for Hardware-based Control-Flow Integrity Monitoring}.  International Conference on Reconfigurable Computing and FPGAs (ReConFig), December 2018.

\item{\it Semantics-directed Prototyping of Hardware Runtime Monitors}. The 29th International Symposium on Rapid System Prototyping (RSP), October 2018.

\item{\it Why Functional Hardware Description Matters.}
Oak Ridge National Laboratory, Oak Ridge TN, 3/13/2017.


\item{\it Model-driven Design \& Synthesis of the SHA-256 Cryptographic Hash Function in ReWire.} The 27th International Symposium on Rapid System Prototyping (RSP), 2016.

\item{\it A Programming Model for Reconfigurable Computing Based in Functional Concurrency.} The 11th International Symposium on Reconfigurable Communication-centric Systems-on-Chip (ReCoSoC 2016).

\item{\it Provably Correct Development of reconfigurable hardware designs via equational reasoning.} The 2015 International Conference on Field-Programmable Technology (FPT 2015).

\item{\it High Assurance Hardware with ReWire: Just Say No! to Semantic Archaeology.}
The Technical Cooperation Program (TTCP) workshop, Defence Science \& Technology Organization (DSTO), Adelaide Australia, 5/18/2015.



%\thispagestyle{fancyplain}
%\fancyhf{}
%\renewcommand{\headrulewidth}{0pt}
%\chead{ \fancyplain{}{{\bf\large{ Invited Talks and Conference Presentations (cont'd)} }}}
%\cfoot{ \fancyplain{}{\thepage} }

%%%%%%%%%%%%
%%%%%%%%%%%%
%%%%%%%%%%%%
%%%%%%%%%%%%
%\section{Invited Talks and Conference Presentations (cont'd)}


\item{\it High Assurance Hardware with ReWire: Just Say No! to Semantic Archaeology.}
High Confidence Software and Systems (HCSS) NSA workshop, Annapolis MD, 5/6/2015.

\item{\it High Assurance Hardware with ReWire: Just Say No! to Semantic Archaeology.}
Oak Ridge National Laboratory, Oak Ridge TN, 3/3/2015.

\item{\it The Confinement Problem in the Presence of Faults.} Proceedings of the 2012 International Conference on Formal Engineering Methods.

\item{\it Towards semantics-directed system design and synthesis.}
International Conference on
  Engineering Reconfigurable Systems and Algorithms (ERSA), 7/19/2011.
  
\item{\it Understanding Security Flows in the Many Core Era.}
National Security Agency, Information Assurance Directorate, 
10/14/2010, Sponsor: Brad Martin.

\item{\it An Academic Response to National Science and Technology Challenges.}
Department of Defense Intelligence Information Systems (DoDIIS) Worldwide Conference, 5/26/2010.

\item{\it Model-driven Synthesis of High Assurance Secure Systems.} University of Iowa, 10/23/09, Sponsor: Professor Aaron Stump.

\item{\it Model-driven Synthesis of High Assurance Secure Systems.} Galois, Inc., 5/20/08, Sponsor: John Launchbury.
%\end{itemize}


\item{\it Compiling for Security.} Missouri Institute of Technology (formerly University of Missouri, Rolla), 4/28/08, Sponsor: Professor Bruce McMillen.

\item{\it Proof Abstraction for Imperative Languages.} The 4th Asian Symposium on Programming Languages and Systems (APLAS06), Sydney, Australia, 11/8/2006. 

\item{\it The Essence of Multitasking.} The 11th International Conference on Algebraic Methodology and Software Technology (AMAST06), Kuuresaare, Estonia, 7/5/06.

\item{\it Domain-specific Languages for Cellular Interactions.} University of Kansas, 4/29/05, Sponsor: Professor Perry Alexander. 

\item{\it A Simple Semantics for Polymorphic Recursion.}, Proceedings of the 3rd Asian Symposium on Programming Languages and Systems (APLAS05), Tsukuba, Japan, 11/3/2005.

\item{\it Achieving Information Flow Security Through Precise Control of Effects.} The 18th IEEE Computer Security Foundations Workshop (CSFW05), Aix-en-Provence, France, 7/20/05.

\item{\it Information-flow Security \& Monadic Effects.}
University of Illinois at Urbana-Champaign, 4/18/2005, Sponsor:
Professor Jos\'{e} Meseguer.

\item{\it Domain-specific Languages for Cellular Interactions.} The 26th Annual IEEE International Conference on Engineering in Medicine and Biology, San Francisco, California, 9/3/04.

\item{\it Domain-specific Languages for Biology.} Georgia State
  University, 5/26/2004, Sponsor: Professor Yi Pan.


%\thispagestyle{fancyplain}
%\fancyhf{}
%\renewcommand{\headrulewidth}{0pt}
%%\chead{ \fancyplain{}{{\bf\large{ Invited Talks and Conference Presentations (cont'd)} }}}
%%\cfoot{ \fancyplain{}{\thepage} }


\item{\it Domain Separation by Construction.} LICS03 Satellite Workshop on Foundations of Computer Security (FCS03), Ottawa, Canada, 6/26/03. 

\item{\it Prospects for Modular Compilation.}
Rice University, 12/11/2002, Sponsor: Professor Walid Taha.

\item{\it Domain-specific Languages for Compilation.}
University of Alabama, 11/22/2002, Sponsor: Professor Joel Jones.

\item{\it Pattern-driven Reduction in Haskell.} Second International Workshop on Reduction Strategies in Rewriting and Programming, Copenhagen, Denmark, 7/21/02.

\item{\emph{Fine Control of Demand in Haskell.}} The Sixth International Conference on the Mathematics of Program Construction (MPC02), Dagstuhl, Germany, 7/8/02. 

\item{\it Dynamically Adaptable Software with Metacomputations in a Staged Language.} The Second Workshop on the Semantics, Applications and Implementation of Program Generation (SAIG01), Florence, Italy, 9/6/01. 

\item{\it Metacomputation-based Compiler Architecture.} The Fifth International Conference on the Mathematics of Program Construction (MPC00), Ponte de Lima, Portugal. 7/5/00. 

\item{\it Modular Compilers Based on Monad Transformers.} The IEEE International Conference on Computer Languages (ICCL98), Chicago, Illinois. 5/16/98.

\end{enumerate}


%\newpage
%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%
\section*{Students \& Postdocs Supervised}
%\thispagestyle{fancyplain}
%\fancyhf{}
\subsection*{Postdoctoral Researchers Supervised}

\begin{enumerate}[leftmargin=0.0mm]
\item Adam Procter. 1/2015-5/2016.
\item Soumya Sanyal. 9/2013-9/2015.
\end{enumerate}

\subsection*{Graduated Ph.D Students}

\begin{enumerate}[leftmargin=0.0mm]
\item Adam Procter. GAANN fellow. Graduated: 12/2014.\\
\newblock Dissertation: \emph{Semantics-directed Design and Implementation of High Assurance Hardware}.

\item Ian Graves. Graduated: 12/2015.\\
\newblock Dissertation: \emph{Device-level Composition in ReWire}.


\item Christopher Hathhorn. GAANN Fellow. Graduated: 12/2017.\\
\newblock Dissertation: \emph{Defining the Undefinedness of C11: Practical Semantics-based Program Analysis}.

\item Thomas Reynolds. Graduating 12/13/2019. \\
\newblock Dissertation: \emph{Mechanizing the Metatheory of ReWire}.


\end{enumerate}

\subsection*{Graduated MS Students}

\begin{enumerate}[leftmargin=0.0mm]
\item Daniel Dunn. Thesis: Penetration Testing FOSCAM IP Cameras. Graduated: 5/2018.
\item Zolbayar Magsar. Graduated: 5/2016.
\item Richard Wallen. Graduated: 12/2015.
\item Mohammed Alharbi. Graduated: 5/2013.
\item Jared Kvanvig. Thesis: Compiler Infrastructure for the Cheap Threads Compiler. Graduated: 12/2009.
\item Ajay Nagar.  Non-thesis. Graduated: 5/2009.
\item Megha Rao. Thesis: Physical Security in a Nuclear Environment. Graduated: 12/2008.
\item Pericles S. Kariotis. Thesis: Making Monads First-class Using Template Haskell. Graduated: 12/2008.
\end{enumerate}

%\thispagestyle{fancyplain}
%\fancyhf{}
%\renewcommand{\headrulewidth}{0pt}
%\chead{ \fancyplain{}{{\bf\large{ Students and Postdocs Supervised (cont'd)} }}}
%\cfoot{ \fancyplain{}{\thepage} }

%\newpage
%%%%%%%%%%%
%%%%%%%%%%%
%%%%%%%%%%%
%%%%%%%%%%%
\section*{References}
\vspace{1ex}

Available by request.


%\begin{minipage}[t]{3.1in}
%\begin{flushleft}
%Dr. Gerard Allwein\\
%Center for High Confidence Systems\\
%Formal Methods Section (5543)\\
%US Naval Research Laboratory\\ 
%Washington, DC  \\
%Phone: (202) 404-3748 \\
%Email: \href{mailto:gerard.allwein@nrl.navy.mil}{gerard.allwein@nrl.navy.mil}
%\end{flushleft}
%\end{minipage}
%\begin{minipage}[t]{3.1in}
%\begin{flushleft}
%Professor Michela Becchi\\
%Dept. of Electrical and Computer Engineering\\
%North Carolina State University\\
%Phone: (573) 823-5537\\
%Email: \href{mailto:mbecchi@ncsu.edu}{mbecchi@ncsu.edu}
%\end{flushleft}
%\end{minipage}
%
%\vspace{3ex}
%
%\begin{minipage}[t]{3.1in}
%\begin{flushleft}
%Professor David Andrews\\
%Dept. of Computer Science Engineering \\
%University of Arkansas\\ 
%Fayetteville, Arkansas 72701 \\
%Phone: (479) 575-4394 \\
%Email: \href{mailto:dandrews@uark.edu}{dandrews@uark.edu}
%\end{flushleft}
%\end{minipage}
%\begin{minipage}[t]{3.1in}
%\begin{flushleft}
%Professor Rohit Chadha\\
%Electrical Engineering \& Computer Science Department \\
%University of Missouri\\
%Columbia, MO 65209\\
%Phone:  (573) 882-3843 \\
%Email: \href{mailto:chadhar@missouri.edu}{chadhar@missouri.edu}
%\end{flushleft}
%\end{minipage}
%
%\vspace{3ex}
%
%\begin{minipage}[t]{3.1in}
%\begin{flushleft}
%Dr. Gregory Shannon\\
%Chief Cybersecurity Scientist\\
%Idaho National Laboratory\\ 
%Idaho Falls, ID   83415\\
%Phone: (614) 216-7546 \\
%Email: \href{mailto:Gregory.Shannon@inl.gov}{Gregory.Shannon@inl.gov}
%\end{flushleft}
%\end{minipage}


\end{document}
